---
title: "Off-Label & Off-Guideline Project"
author: "Alex Paynter"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: 
  html_document:
    toc: true
    toc_float: false
    theme: paper
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  include = F,
  warning = F,
  message = F,
  fig.width = 7,
  fig.height = 5
)
```





```{r}
library(fs); library(purrr); library(here);
purrr::walk(.x = fs::dir_ls(here("R")), .f = source)
```

```{r}
gdtools::register_gfont('Roboto')
set_flextable_defaults(
  font.size = 10,
  theme_fun = theme_booktabs,
  font.family = 'Roboto'
)


dt_wrapper <- function(x) {
  DT::datatable(
    x,
    style = "bootstrap4",
    fillContainer = F
  )
}
    

```


## Introduction

This is a working document for analyses related to the Off-label & Off-guideline manuscript chaired by Jeremy Warner.

The regimen/drug data is filtered in all tables to **exclude Investigational Drugs**.

### Cohort filters

Filtering of the raw BPC data we will apply to all items except for R1.1:

- Only participants with a **single** cancer diagnosis are included ("first and only" cancers in GENIE BPC).
- Only US sites will be considered (we have a small number in Canada in BPC).

Pre-processing of the data that will apply to all tables and figures:

- "Non-standard" drug administration routes will be eliminated when known.
  - Our definition of standard and nonstandard comes from the `drugs_admin` variable.  
  - This variable is **not populated for the pancreas, prostate and NSCLC cohorts**, but only for bladder, breast and colorectal.  This means that we cannot exclude non-standard routes in those three cohorts unless additional rules are added.
  - The two biggest examples of drugs with non-standard routes are BCG vaccine (intravesical in bladder cohort) and Floxuridine (other route in CRC).
  - Standard routes are "orally, intravenously or by infusion".
  - Non-standard routes are "Intraperitoneal (direct into the abdominal cavity), Intrapleural (direct into the pleural space around the lung), Intralesional (direct into a lesion), Intrathecal (by spinal catheter), Intravesical (bladder installation), Other."
- We will also just completely ignore some drugs due to the lack of perfection in the `drugs_admin` variable.  These are currently BCG Vaccine, BCG Solution and Floxuridine.
  
**Definitions:**

- *index cancer* - The cancer diagnosis that qualified the participant for curation into a BPC cohort (e.g. to be in the prostate cohort you must have a prostate cancer matching a set of Oncotree codes).
- *F&O* - First and only cancer diagnosis.  Meaning that the only known cancer for this participant was the one that qualitified them for inclusion in a GENIE BPC cohort.
- *repeat regimens* - If a participant has a regimen with drugs {A,B,C} and the very next regimen in their record is {A,B,C} again, that second regimen is a repeat regimen.  If they use {A,B,C,D} or {A,B} in their next regimen that doesn't count.



```{r}
dft_all_cases <- readr::read_rds(
  here('data', 'no_ca_seq_filter', 'clin_dat_wide.rds')
)

dft_cohort_cases <- readr::read_rds(
  here('data', 'cohort', 'clin_dat_wide.rds')
)

dft_filtering_impact <- bind_rows(
  mutate(summarize_cohort(dft_all_cases), filt = "Raw"),
  mutate(summarize_cohort(dft_cohort_cases), filt = "First & Only")
)

dfp_filtering_impact <- dft_filtering_impact %>%
  pivot_longer(
    cols = -c(cohort, filt),
    names_to = "quantity"
  )  %>%
  pivot_wider(
    names_from = "cohort",
    values_from = "value"
  ) %>%
  select(quantity, filt, everything()) 

dfp_filtering_impact %<>%
  mutate(quantity = forcats::fct_inorder(quantity)) %>%
  arrange(quantity, desc(filt))
```


```{r}
# need to load the crosswalks so we can report them out:
dft_cw_condition <- readr::read_rds(
  here('data', 'warner_materials', 'cw_condition.rds')
)
dft_cw_drug <- readr::read_rds(
  here('data', 'warner_materials', 'cw_drug.rds')
)
dft_ind_mapped <- readr::read_rds(
  here('data', 'warner_materials', 'indications_mapped.rds')
)
```


```{r}
dft_hdrug_det <- readr::read_rds(
  here('data', 'linked_approvals', 'hdrug_determinations.rds')
)
```




## Ch 1 - BPC data description

### R1.1 Cohort filtering impact

Now that we're filtering to F&O, we have some room to describe additional quanitites of our cohort filtering.  Four quantities are shown:

- `n_pts` - The number of unique patients.
- `n_cancers` - The number of cancers in those patients.  Note that this is the same for the First & Only cohort because each person has exactly one cancer.
- `n_reg` - The number of regimens, using the unaltered definition used in GENIE BPC.  This does not include invesigational 
- `n_unique_drug` - The number of unique drugs observed among all the regimens.

```{r, include = T}
dfp_filtering_impact %>%
  flextable(.) %>%
  flextable::merge_v(j = 'quantity') %>%
  flextable::fix_border_issues(.) %>%
  flextable::valign(j = 'quantity', valign = 'top') %>%
  flextable::bg(i = c(2,4,6,8), bg = '#e6ecf2')
```

From this point on the tables deal only with the *First & Only* cases.




```{r}
dft_hreg_cohort <- dft_cohort_cases %>%
  select(hreg) %>%
  unnest(hreg) %>%
  fix_cohort_names(.)

dft_hdrug_cohort <- dft_cohort_cases %>%
  select(cohort, hdrug) %>%
  unnest(hdrug)
```




```{r}
dfp_reg_sum <- dft_hreg_cohort %>%
  group_by(cohort, regimen_drugs) %>%
  summarize(
    n_regimens = n(),
    n_people = length(unique(record_id)),
    .groups = "drop"
  )
```


```{r, write_excel_data_reg, include = F}
dfp_reg_sum %>%
  arrange(cohort, regimen_drugs) %>%
  readr::write_csv(
    x = .,
    file = here('output', 'regimen_counts_by_cohort.csv')
  )
```

### R1.2a Drugs used (as regimens)

See the **attached CSV** (regimen_counts_by_cohort.csv) for the full list of regimens observed in each cohort.  Again, this does not include any regimens with investigational agents, and we have filtered each group to F&O cancers.

For convenience, the following table supports simple text searching (not case sensitive).  For example, if you type "Carboplatin bladder" you should see all summaries for the drug carboplatin in the bladder cohort.

Each row shows the number of regimens with those drugs we have in the data (`n_regimens`) and the number of people who had at least one regimen with those exact drugs (`n_people`).

```{r print_reg_table, show = T, include = T}
dt_wrapper(dfp_reg_sum)
```




```{r}
dfp_drug_sum <- dft_hdrug_cohort %>% 
  group_by(cohort, agent) %>%
  summarize(
    n_uses = n(),
    n_people = length(unique(record_id)),
    .groups = "drop"
  )
```

```{r, write_excel_data_drug, include = F}
dfp_drug_sum %>%
  arrange(cohort, agent) %>%
  readr::write_csv(
    x = .,
    file = here('output', 'drug_use_counts_by_cohort.csv')
  )
```

### R1.2b Drugs used (as drugs)

The following content is the same information as the previous table, counted as separate drugs (agents) rather than using the BPC regimen rules.  Each row shows the number of regimens which used that drug in the data (`n_uses`) and the number of people who had at least one regimen using this agent (`n_people`).

See the **attached CSV** (drug_use_counts_by_cohort.csv) for the full list of drugs observed in each cohort.  


```{r print_drug_table, show = T, include = T}
dt_wrapper(dfp_drug_sum)
```


```{r}
# fxd = first x days analyses
dft_hdrug_fxd <- dft_hdrug_cohort %>%
  group_by(record_id, ca_seq) %>%
  mutate(
    dx_first_drug_use_int = min(dx_drug_start_int, na.rm = T)
  ) %>%
  ungroup(.)

dfp_first_drug_sum <- dft_hdrug_fxd %>%
  filter_drugs_first_x_days(
    ., 
    x = 0, # within 0 days to start.
    var_index_time = 'dx_first_drug_use_int'
  ) %>%
  group_by(cohort, agent) %>%
  summarize(
    # n_uses should be the same as n_people here.
    n_people = length(unique(record_id)),
    .groups = "drop"
  )

dfp_first_30d_drug_sum <- dft_hdrug_fxd %>%
  filter_drugs_first_x_days(
    ., 
    x = 30, # within 30 days.
    var_index_time = 'dx_first_drug_use_int'
  ) %>%
  group_by(cohort, agent) %>%
  summarize(
    # n_uses should be the same as n_people here.
    n_people = length(unique(record_id)),
    .groups = "drop"
  )
```


### R1.3a First drugs used

Drugs which constitute the first recorded start date for each participant.  `n_uses` and `n_people` should be identical here, so we just state the latter.  If two drugs are started at the same time, both would appear in this table.

BPC regimen encoding does not factor into this table at all - we're examining drugs as separate entities and only looking at the time they were started.

```{r, print_first_drug_sum, include = T}
dt_wrapper(dfp_first_drug_sum)
```

### R1.3b Drugs used within 30 days of first

Drugs used within 30 days of the first drug use.  Similar to the previous table but allowing a 30 day window for the second drug start time.

```{r, print_first_30d_drug_sum, include = T}
dt_wrapper(dfp_first_30d_drug_sum)
```


```{r}
dft_second_drug_t_dist <- dft_hdrug_fxd %>%
  mutate(
    sec_drug_diff = dx_drug_start_int - dx_first_drug_use_int
  ) %>%
  filter(
    abs(sec_drug_diff) > 0.5
  ) %>%
  arrange(sec_drug_diff) %>%
  group_by(record_id, ca_seq) %>%
  slice(1) %>%
  ungroup(.)


gg_sec_drug_t <- plot_time_dist_violin_ecdf(
  dat = dft_second_drug_t_dist,
  time_var = "sec_drug_diff",
  time_var_lab = "Second drug start interval (days from first drug)",
)

gg_sec_drug_t_400 <- plot_time_dist_violin_ecdf(
  dat = dft_second_drug_t_dist,
  time_var = "sec_drug_diff",
  time_var_lab = "Second drug start interval (days from first drug)",
  x_coord_cap = 400
)

```


### R1.3c Second drug start interval distribution

The quantity being displayed here is the time from the start of the first drug to the start of the second drug in days (excluding those started on the same day as the first drug).  

For example, if someone started drug A on day 0, drug B on day 0, and drug C on day 28, this plot would show the difference between drugs A and C, 28 days (repeated for all participants).

```{r, include = T, fig.height = 3}
gg_sec_drug_t
```

A version of the same plot zooming in on the first year (approximately), where most of the action is:

```{r, include = T, fig.height = 3}
gg_sec_drug_t_400
```




```{r}

dft_met_timing <- dft_cohort_cases %>%
  mutate(
    met_timing = purrr::map(
      .x = ca_ind,
      .f = (function(x) {
        make_dmet_status_block(x) %>%
          filter(
            dmet_status %in% "Distant Metastasis"
          ) %>%
          # years -> days
          mutate(dx_met_days = dx_block_start * 365.25) %>%
          select(
            record_id,
            ca_seq,
            dx_met_days
          )
      })
    )
  ) %>%
  select(cohort, met_timing) %>%
  unnest(met_timing)

dft_hdrug_met <- left_join(
    dft_hdrug_cohort,
    dft_met_timing,
    by = c("cohort", "record_id", "ca_seq")
  )

dft_hdrug_met %<>%
  # only cases where a metastasis was noted
  filter(!is.na(dx_met_days)) %>%
  mutate(dmet_drug_start_int = dx_drug_start_int - dx_met_days) %>%
  # only drugs started on or after the time of metastasis
  filter(dmet_drug_start_int > -0.1) 

dft_hdrug_met %<>%
  group_by(cohort, record_id, ca_seq) %>%
  mutate(
    dmet_first_drug_int = min(
      dmet_drug_start_int, 
      na.rm = T
    )
  ) %>%
  ungroup(.)


```


```{r}
dfp_first_drug_met_sum <- dft_hdrug_met %>%
  filter_drugs_first_x_days(
    ., 
    x = 0, # within 0 days to start.
    var_index_time = 'dmet_first_drug_int'
  ) %>%
  group_by(cohort, agent) %>%
  summarize(
    # n_uses should be the same as n_people here.
    n_people = length(unique(record_id)),
    .groups = "drop"
  )

```


### R1.4a First drugs used (metastatic setting)

This only examines drugs started on or after a metastatic diagnosis (de novo or not), and of course only in patients where that diagnosis was made at some point.

As with the previous plots, if a second drug was started on the same day as the first drug, it will appear in this table.


```{r, include = T}
dt_wrapper(dfp_first_drug_met_sum)
```

Note:  This list has about 70% as many rows (combinations of cohort and agent) as the one for all participants in this cohort.


## Ch 2 - Lines of therapy 

### R2.1 Rules for building lines 

*Note: This deals with patients of all stages for the moment.  I know that's an abuse of the term "lines of therapy" but I'm just trying to address the strategy for restacking drugs into therapy lines.

At our October meeting we discussed the intricacies of BPC cancer regimens and how they can be overlapping, ajoining, etc. depending on the type of therapy addressed.  Jeremy proposed a simple start for this:

- The first line is the first aggregation of anti-cancer therapies.  This means that they must overlap, but they do not need to start on the same day.

After looking into the regimen data a bit further I would suggest that we need some pre-processing steps as well.  These include:

1. For two drug uses that start and end on adjoining days, or overlap further, we should join them into one "use".  
  - Examples:  GENIE-DFCI-008121 in the CRC cohort, regimens 2 and 3. GENIE-DFCI-053242 for bicalutamide below.
2. Any drug uses of zero days (to the best of our knowledge) should be eliminated.  I believe many of these just appear to be zero days because there is not yet a confirmed discontinuation date.
  - Examples:  GENIE-DFCI-007616 in the NSCLC cohort, regimen 3.
  
#### Example case #1

The following plot is **interactive** - hover over each rectangle for more information.  The colors are the GENIE BPC regimen number.

This person's first line would be a four drug regimen, which happens to be their regimen 1 in GENIE BPC.

```{r, include = T}
dft_hdrug_cohort %>%
  filter(record_id %in% 'GENIE-MSK-P-0020681') %>%
  plot_drug(., return_plotly = T)
```

**Proposed handling:** This person's first line would be a four drug regimen of Floxuridine and the 3 drugs that are part of BPC regimen #2.

#### Example case #2

```{r, include = T}
dft_hdrug_cohort %>%
  filter(record_id %in% 'GENIE-DFCI-053242') %>%
  plot_drug(., return_plotly = T)
```

**Proposed handling:** This example would combine the Bicalutamide regimen's into one use in preprocessing.  The first line would be docetaxel, leuprolide and bicalutamide.  The Abiraterone Acetate administration would not cound in the first line because the docetaxel administration ended before this was started.


  
```{r, include = F}

dft_hreg_cohort %>% 
  filter(record_id %in% 'GENIE-VICC-116953')

dft_overlap_cases <- tribble(
  ~cohort, ~record_id, 
  'Breast', "GENIE-DFCI-000701", # possible sequence, not overlapping
  'Breast', 'GENIE-VICC-568921', # possible sequence, not overlapping
  'CRC', 'GENIE-VICC-116953', # stop/start lots
  'CRC', "GENIE-MSK-P-0007135", # stop/start lots
  'Pancreas', 'GENIE-MSK-P-0010984', # large buildup
  'CRC', 'GENIE-VICC-499960', # all over
) %>%
  mutate(ca_seq = 0)


dft_over_ex <- dft_overlap_cases

dft_over_ex %<>%
  mutate(
    drug_sub_case = purrr::pmap(
      .l = list(c = cohort, r = record_id, s = ca_seq),
      .f = \(c,r,s) {
        dft_hdrug_cohort %>%
          filter(
            cohort %in% c &
              record_id %in% r & 
              ca_seq %in% s
          )
      }
    )
  ) %>%
  mutate(
    gg_drug_case = purrr::map(
      .x = drug_sub_case,
      .f = plot_drug
    )
  )

dft_over_ex %<>%
  mutate(
    plt_drug_case = purrr::map(
      .x = gg_drug_case,
      .f = \(x) {
        plotly::ggplotly(x, tooltip = 'text')
      }
    )
  )
  


```

### R2.2 Interesting cases to consider

#### Possible sequence, not overlapping

It's common in the breast cancer cohort to see a (seemingly planned) progression of drugs coded as one regimen, but they're not technically overlapping:

```{r, include = T}
dft_over_ex$plt_drug_case[[1]]
```


```{r, include = T}
dft_over_ex$plt_drug_case[[2]]
```

#### Many stops and starts

This is especially common in the CRC cohort:

```{r, include = T}
dft_over_ex$plt_drug_case[[3]]
```

```{r, include = T}
dft_over_ex$plt_drug_case[[4]]
```

This begs the question of whether we want to combine drug administrations which are close but not quite overlapping.

#### Large buildup of for one line

Occasionally someone would qualify for something like a 7-drug regimen:

```{r, include = T}
dft_over_ex$plt_drug_case[[5]]
```

#### Generally complex

```{r, include = T}
dft_over_ex$plt_drug_case[[6]]
```




## *Ch 3 - Joining to indications

### *R3.0 Linkage Strategy

To generate a list of potential approvals we will join two datasets:

- Jeremy Warner's indications sheet, which lists about 3000 rows of approvals over several regulatory agencies.
- The regimen BPC data, reshaped to be one row per drug rather than one row per regimen.  Filtering described in chapter 1 generally applies.
  - Additionally, we excluded **any drug approved before 1997** as those labels tend to be discordant with practice. 

The concepts we are joining on are:

- Warner's `condition` is mapped to BPC `cohort`.
- Warner's `component` is mapped to BPC `agent`.  `agent` is a reshape of drug names from the `regimen_drugs` column.

Obviously the text representations of these two concepts are slightly different, so we need some crosswalks to link them.  

#### Crosswalk: Conditions

```{r, include = T}
dft_cw_condition %>%
  flextable(.) %>% 
  autofit(.)
```

All other `condition` entries from the Warner list are unmapped/unused.  The full list of unused conditions is in an appendix.

#### Crosswalk: Component (drug)

Reminder: `agent` is directly pulled GENIE BPC's `regimen_drugs` after splitting up the drugs.  `component` is from Warner's indications sheet.

```{r, include = T}
dft_cw_drug %>%
  select(component, agent, agent_map_type) %>%
  dt_wrapper(.)
```

Notes:

- `agent_map_type` is just a short description of the strategy I used to make the link.  The levels are:
  - `exact`: The strings were a perfect (case-ignoring) match.
  - `trimmed`:  After trimming common suffixes from the BPC data (like "sulfate", "acetate") the strings were a perfect match.
  - `manual`:  Manual link, by someone with no medical or pharmacology training (!).
  



```{r}
vec_bpc_drugs <- dft_hdrug_det %>%
  pull(agent) %>%
  unique

vec_ind_drugs <- dft_ind_mapped %>%
  filter(mapped_agent %in% vec_bpc_drugs) %>%
  pull(mapped_agent) %>%
  unique

prop_uses_covered <- dft_hdrug_det %>%
  mutate(
    drug_in_ind = agent %in% vec_ind_drugs
  ) %>% 
  summarize(
    prop_uses_covered = mean(drug_in_ind, na.rm = T)
  ) %>%
  pull(prop_uses_covered) 


vec_bpc_drugs_not_mapped <- vec_bpc_drugs[!(vec_bpc_drugs %in% vec_ind_drugs)] %>% 
  sort %>%
  paste(., collapse = ", ")

```

### *Crosswalk success

- Of the `r length(vec_bpc_drugs)` unique drugs in our BPC cohorts, `r n_pct_str(length(vec_ind_drugs %in% vec_bpc_drugs), length(vec_bpc_drugs), show_d = F)` were found in the indications sheet after mapping.
  - The agents which we couldn't map to anything in the indications sheet are: `r vec_bpc_drugs_not_mapped`.  All used very few times in BPC.
- Of the `r nrow(dft_hdrug_det)` uses of a drug (one person using a drug for one block of time), `r round(prop_uses_covered*100, 3)`% involve a drug which was successfully mapped to a drug in the indications sheet.



```{r}
dft_off_label_uses <- dft_hdrug_det %>%
  count_off_label(.) %>%
  filter(n_off_label > 0)

dft_hdrug_det_first_day <- dft_hdrug_fxd %>%
  filter_drugs_first_x_days(
    ., 
    x = 0, # within 0 days to start.
    var_index_time = 'dx_first_drug_use_int'
  ) %>%
  select(cohort, record_id, ca_seq, regimen_number, drug_number) %>%
  left_join(
    .,
    dft_hdrug_det,
    by = c('cohort', 'record_id', 'ca_seq', 'regimen_number', 'drug_number')
  )
    
dft_off_label_uses_first_drug <- dft_hdrug_det_first_day %>%
  # This drops the excluded drugs from link_drugs_indications.R
  filter(agent %in% dft_hdrug_det$agent) %>%
  count_off_label(.) %>%
  filter(n_off_label > 0)

```
  
### R3.1 Off label use definition

Our definition of an on-label use is currently any use of a drug which has a matching row in the indications sheet that meets the following criteria:

1. A matching indication exists, meaning:

  - Regulator for the approval is FDA.
  - Condition maps to the BPC cohort of the drug use.
  - Component maps to the BPC agent (regimen drug) of the drug use.
  
2. If the indication a requires metastatic state, the drug use started after a metastatic diagnosis.

3. The drug start date is after the approval date for the drug.  Notes:

  - We do not have exact dates in GENIE BPC.  We calculate the maximum drug start date given a participant's `birth_year` (whole years) and the interval from birth date to start of the drug (an exact number of days) by assuming they were born on Dec 31.
  - Assuming people were born as late as possible is conservative in that we consider the fewest number possible off-label by date.
  - A later section will deal with the opposite assumption (taking the minimum possible drug start date).

Planned expansions to this definition include:

- Additional indications for non-cohort things like TMB for pembrolizumab.

**Off-label** use is a drug use which can't be verified as on-label according to the definition above under any indication in our sheet.

Each off label use is assigned a single "reason" it's off label, which means we have a priority system.  The following order is used:

- **No indications found** - There was no cancer type indication at all for this drug use.
- **Not metastatic at use** - The applicable drug indication required metastases at use and the participant did not have distant mets recorded when the drug was started.
- **Started before approval** - The drug was started before the approval date.

For example, if a participant uses a drug in 2015 while not metastatic, and the drug required metastases with it's only approval in 2017, that will count as "Not metastatic at use" (higher priority).  These can be shifted around, except for "no indication found".



```{r}

# Just a rename:
dft_hdrug_det %<>% 
  mutate(off_label_type = failure_type_f)

dfp_olu_cohort <- dft_hdrug_det %>%
  count_off_label(group_vars = c('cohort')) %>%
  mutate(
    off_label_uses = n_pct_str(n_off_label, n_uses, show_d = T)
  ) %>%
  select(-c(n_uses, n_on_label, n_off_label, prop_off_label)) %>%
  flextable(.) %>%
  autofit(.)

dfp_olu_type <- dft_hdrug_det %>%
  filter(!valid_ind_exists) %>%
  count(off_label_type) %>%
  flextable(.) %>%
  autofit(.)

dfp_olu_cohort_type <- dft_hdrug_det %>%
  count(off_label_type, cohort) %>%
  complete(
    data = .,
    off_label_type, cohort,
    fill = list(n = 0)
  ) %>%
  pivot_wider(
    names_from = cohort,
    values_from = n
  ) %>%
  mutate(
    off_label_type = replace_na(
      as.character(off_label_type), 
      "(on label)"
    )
  ) %>%
  flextable(.) %>%
  autofit(.) %>%
  flextable::color(i = 4, color = "gray50")
  
```

### R3.2 Off label use overview

By cohort (denominators show the number of total drug uses included):

```{r, include = T}
dfp_olu_cohort
```

By reason (see notes on prioritization above):

```{r, include = T}
dfp_olu_type
```

Crosstabulation between those two.  The bottom row shows the number of on-label uses.

```{r, include = T}
dfp_olu_cohort_type
```







```{r}
simple_olu_disp_help <- function(
    dat_olu
) {
  dat_olu %>%
    mutate(off_label_uses = n_pct_str(n_off_label, n_uses, show_d = T)) %>%
    select(-c(n_uses, n_on_label, n_off_label, prop_off_label)) %>%
    flextable(.) %>%
    autofit(.)
}

dft_hdrug_det %>%
  count_off_label(group_vars = c('cohort')) %>%
  simple_olu_disp_help(.)

dft_hdrug_det %>%
  filter(!valid_ind_exists) %>%
  count(failure_type_f)
```
























```{r, include = T}
dft_off_label_uses %>%
  mutate(
    pct_off_label = round(prop_off_label * 100)
  ) %>%
  select(cohort, agent, n_off_label, pct_off_label) %>%
  dt_wrapper(.)
```

Notes:

- There are some obvious problems here - see the table below for more info on *how* some of these are declared off label.




```{r}
dft_off_label_reasons <- dft_hdrug_det %>% 
  count(cohort, agent, failure_type_f) %>%
  filter(!is.na(failure_type_f)) %>%
  group_by(failure_type_f) %>%
  arrange(desc(n)) %>%
  slice(1:5) %>%
  ungroup(.)

```

### *R3.1b Off-label reasons

The following table shows the top 5 off label uses for our two ways a use can be declared off label:

```{r, include = T}
dft_off_label_reasons %>%
  select(reason = failure_type_f, everything()) %>%
  flextable(.) %>%
  merge_v(j = 1) %>% 
  valign(j = 1, valign =  'top') %>%
  autofit(.) %>%
  fix_border_issues(.)
```







### *R3.2 Off label use, first drug

The following table is the same as the previous one, except we limit to only the first day of drug use by each person:
 
```{r, include = T}
dft_off_label_uses_first_drug %>%
  mutate(
    pct_off_label = round(prop_off_label * 100)
  ) %>%
  select(cohort, agent, n_off_label, pct_off_label) %>%
  dt_wrapper(.)
```
 



```{r}
dft_reg_num_off_label <- dft_hdrug_det %>%
  group_by(record_id, regimen_number) %>%
  summarize(
    any_off_label = as.numeric(any(valid_ind_exists %in% F)),
    .groups = "drop"
  )
  # ) %>%
  # group_by(regimen_number) %>%
  # summarize(
  #   n_off = sum(any_off_label),
  #   n_total = n(),
  #   .groups = "drop"
  # ) %>%
  # mutate(
  #   prop_off_label = n_off / n_total
  # )

gg_smooth <- ggplot(
  dft_reg_num_off_label,
  aes(y = any_off_label, x = regimen_number)
) + 
  geom_smooth(color = "#3e5622", fill = "#95A683") +
  scale_x_continuous(
    breaks = seq(1, 101, by = 10),
    name = "BPC Regimen number"
  ) +
  scale_y_continuous(
    name = "Proportion",
    breaks = seq(0, 100, by = 5) / 100,
    labels = paste0(seq(0, 100, by = 5), "%"),
    expand = c(0,0)
  ) + 
  labs(title = "Proportion of subjects with any off label use (penalized spline)") + 
  theme_bw() + 
  theme(
    axis.title = element_markdown(angle = 0)
  )
gg_data_density <- ggplot(
    dft_reg_num_off_label,
    aes(x = regimen_number)
) + 
  geom_histogram(binwidth = 1, fill = "#83781B") +
  scale_x_continuous(
    breaks = seq(1, 101, by = 10),
    name = "BPC Regimen number"
  ) +
  scale_y_continuous(
    name = "Obs count",
  ) + 
  theme_bw()

gg_comb <- cowplot::plot_grid(
  gg_smooth,
  gg_data_density,
  ncol = 1,
  rel_heights = c(70,30)
)
  
gg_comb

```


### *R3.3 Later = more off label

We observed previous that first drugs seem to be on label more frequently and hypothesized that later regimens may have more off label use.  The following graph is a rough expansion on that idea:


```{r, include = T}
gg_comb
```

Notes:

- Generally it appears that off label use increases in later regimens.
- We can fix this up to use time rather than regimen number for our reader's ease.  This display was primarily chosen because it was easy to make.




## Indications sheet

The following table shows a few relevant columns from the `indications.csv` sheet.  This is not filtered, so it contains approvals from other regulators and drugs we've excluded from our analysis.

```{r, include = T}
dft_ind_mapped %>% 
  select(component, regulator, date, condition, note, 
         context, stage_or_status) %>%
  dt_wrapper(.)
```



## Issues/concerns

From Nov 21, 2023:

1. Double check that the list of regimens (R1.2) is actually from first and only cancers.  **Confirmed by looking at the `ca_seq` variable for the dataframe.**
2. Confirm that there are no missing drug start times.  **Confirmed, no missing drug start times.  Other info:  About 4% of drugs have a missing `dx_drug_end_int` and vanishingly few (<0.01%) have a missing `dx_drug_end_or_lastadm_int`**


### Unused conditions

The Warner `indications.csv` sheet contains many conditions which didn't seem to map to any BPC cohort are:

```{r, include = T}
dft_ind_mapped %>%
  count(condition) %>%
  distinct(.) %>%
  filter(!(condition %in% dft_cw_condition$condition)) %>%
  arrange(condition) %>%
  rename(n_rows = n) %>%
  dt_wrapper(.)
```

Notes:

- The most important condition which is excluded is `"<NONE>"`.  We will need to discuss what those rows represent. 
- Not all of these conditions describe a drug used in the BPC, and not all of them describe FDA indications (which is our first target).






## Upcoming work

- Expand to checking for date of approval.
- Remove breast sarcomas (about 15 cases in cohort if I recall).
