---
title: "Off-Label & Off-Guideline Project"
author: "Alex Paynter"
date: "`r format(Sys.Date(), '%d %b %Y')`"
output: 
  html_document:
    toc: true
    toc_float: false
    theme: paper
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = F,
  include = F,
  warning = F,
  message = F,
  fig.width = 7,
  fig.height = 5
)
```





```{r}
library(fs); library(purrr); library(here)
purrr::walk(.x = fs::dir_ls(here("R")), .f = source)
```

```{r}
gdtools::register_gfont('Roboto')
set_flextable_defaults(
  font.size = 10,
  theme_fun = theme_booktabs,
  font.family = 'Roboto'
)


```


## Introduction

This is a working document for analyses related to the Off-label & Off-guideline manuscript chaired by Jeremy Warner.

The regimen/drug data is filtered in all tables to **exclude Investigational Drugs**.

Some important filtering of the raw BPC data we will apply to all items except for R1.1:

- Only participants with a **single** cancer diagnosis are included ("first and only" cancers in GENIE BPC).
  
**Definitions:**

- *index cancer* - The cancer diagnosis that qualified the participant for curation into a BPC cohort (e.g. to be in the prostate cohort you must have a prostate cancer matching a set of Oncotree codes).
- *F&O* - First and only cancer diagnosis.  Meaning that the only known cancer for this participant was the one that qualitified them for inclusion in a GENIE BPC cohort.
- *repeat regimens* - If a participant has a regimen with drugs {A,B,C} and the very next regimen in their record is {A,B,C} again, that second regimen is a repeat regimen.  If they use {A,B,C,D} or {A,B} in their next regimen that doesn't count.



```{r}
dft_all_cases <- readr::read_rds(
  here('data', 'no_ca_seq_filter', 'clin_dat_wide.rds')
)

dft_cohort_cases <- readr::read_rds(
  here('data', 'cohort', 'clin_dat_wide.rds')
)

dft_filtering_impact <- bind_rows(
  mutate(summarize_cohort(dft_all_cases), filt = "Raw"),
  mutate(summarize_cohort(dft_cohort_cases), filt = "First & Only")
)

dfp_filtering_impact <- dft_filtering_impact %>%
  pivot_longer(
    cols = -c(cohort, filt),
    names_to = "quantity"
  )  %>%
  pivot_wider(
    names_from = "cohort",
    values_from = "value"
  ) %>%
  select(quantity, filt, everything()) 

dfp_filtering_impact %<>%
  mutate(quantity = forcats::fct_inorder(quantity)) %>%
  arrange(quantity, desc(filt))
```



## Content

### *R1.1 Cohort filtering impact

Now that we're filtering to F&O, we have some room to describe additional quanitites of our cohort filtering.  Four quantities are shown:

- `n_pts` - The number of unique patients.
- `n_cancers` - The number of cancers in those patients.  Note that this is the same for the First & Only cohort because each person has exactly one cancer.
- `n_reg` - The number of regimens, using the unaltered definition used in GENIE BPC.  This does not include invesigational 
- `n_unique_drug` - The number of unique drugs observed among all the regimens.

```{r, include = T}
dfp_filtering_impact %>%
  flextable(.) %>%
  flextable::merge_v(j = 'quantity') %>%
  flextable::fix_border_issues(.) %>%
  flextable::valign(j = 'quantity', valign = 'top') %>%
  flextable::bg(i = c(2,4,6,8), bg = '#e6ecf2')
```

From this point on the tables deal only with the *First & Only* cases.



```{r}
dfp_reg_sum <- dft_cohort_cases %>% 
  select(cohort, hreg) %>%
  mutate(hreg = purrr::map(
    .x = hreg,
    .f = \(x) select(x, -cohort)
  )) %>%
  unnest(hreg) %>%
  group_by(cohort, regimen_drugs) %>%
  summarize(
    n_regimens = n(),
    n_people = length(unique(record_id)),
    .groups = "drop"
  )
```


```{r, write_excel_data, include = F}
dfp_reg_sum %>%
  arrange(cohort, regimen_drugs) %>%
  readr::write_csv(
    x = .,
    file = here('output', 'regimen_counts_by_cohort.csv')
  )
```

### *R1.2 Regimen drugs

See the **attached CSV** (regimen_counts_by_cohort.csv) for the full list of regimens observed in each cohort.  Again, this does not include any regimens with investigational agents, and we have filtered each group to F&O cancers.

For convenience, the following table supports simple text searching (not case sensitive).  For example, if you type "Carboplatin bladder" you should see all summaries for the drug carboplatin in the bladder cohort.

Each row shows the number of regimens with those drugs we have in the data (`n_regimens`) and the number of people who had at least one regimen with those exact drugs (`n_people`).

```{r print_reg_table, show = T, include = T}
DT::datatable(dfp_reg_sum, options = list(DisplayLength = 25))
```


```{r}
dft_cohort_cases %>%
  select(cohort, hdrug)
```


```{r}
dft_hreg_cohort <- dft_cohort_cases %>%
  select(hreg) %>%
  unnest(hreg) %>%
  fix_cohort_names(.)

dft_hdrug_cohort <- dft_cohort_cases %>%
  select(cohort, hdrug) %>%
  unnest(hdrug)
```


### R1.3 Rules for building lines 

*Note: This deals with patients of all stages for the moment.  I know that's an abuse of the term "lines of therapy" but I'm just trying to address the strategy for restacking drugs into therapy lines.

At our October meeting we discussed the intricacies of BPC cancer regimens and how they can be overlapping, ajoining, etc. depending on the type of therapy addressed.  Jeremy proposed a simple start for this:

- The first line is the first aggregation of anti-cancer therapies.  This means that they must overlap, but they do not need to start on the same day.

After looking into the regimen data a bit further I would suggest that we need some pre-processing steps as well.  These include:

1. For two drug uses that start and end on adjoining days, or overlap further, we should join them into one "use".  
  - Examples:  GENIE-DFCI-008121 in the CRC cohort, regimens 2 and 3. GENIE-DFCI-053242 for bicalutamide below.
2. Any drug uses of zero days (to the best of our knowledge) should be eliminated.  I believe many of these just appear to be zero days because there is not yet a confirmed discontinuation date.
  - Examples:  GENIE-DFCI-007616 in the NSCLC cohort, regimen 3.
  
#### Example case #1

The following plot is **interactive** - hover over each rectangle for more information.  The colors are the GENIE BPC regimen number.

This person's first line would be a four drug regimen, which happens to be their regimen 1 in GENIE BPC.

```{r, include = T}
dft_hdrug_cohort %>%
  filter(record_id %in% 'GENIE-MSK-P-0020681') %>%
  plot_drug(., return_plotly = T)
```

**Proposed handling:** This person's first line would be a four drug regimen of Floxuridine and the 3 drugs that are part of BPC regimen #2.

#### Example case #2

```{r, include = T}
dft_hdrug_cohort %>%
  filter(record_id %in% 'GENIE-DFCI-053242') %>%
  plot_drug(., return_plotly = T)
```

**Proposed handling:** This example would combine the Bicalutamide regimen's into one use in preprocessing.  The first line would be docetaxel, leuprolide and bicalutamide.  The Abiraterone Acetate administration would not cound in the first line because the docetaxel administration ended before this was started.

### R1.4 First LoT

If we apply the rules above we get the following drug aggregations as the first lines of therapy from metastasis: *work in progress*

**WIP**
  
  
```{r, include = F}

dft_hreg_cohort %>% 
  filter(record_id %in% 'GENIE-VICC-116953')

dft_overlap_cases <- tribble(
  ~cohort, ~record_id, 
  'Breast', "GENIE-DFCI-000701", # possible sequence, not overlapping
  'Breast', 'GENIE-VICC-568921', # possible sequence, not overlapping
  'CRC', 'GENIE-VICC-116953', # stop/start lots
  'CRC', "GENIE-MSK-P-0007135", # stop/start lots
  'Pancreas', 'GENIE-MSK-P-0010984', # large buildup
  'CRC', 'GENIE-VICC-499960', # all over
) %>%
  mutate(ca_seq = 0)


dft_over_ex <- dft_overlap_cases

dft_over_ex %<>%
  mutate(
    drug_sub_case = purrr::pmap(
      .l = list(c = cohort, r = record_id, s = ca_seq),
      .f = \(c,r,s) {
        dft_hdrug_cohort %>%
          filter(
            cohort %in% c &
              record_id %in% r & 
              ca_seq %in% s
          )
      }
    )
  ) %>%
  mutate(
    gg_drug_case = purrr::map(
      .x = drug_sub_case,
      .f = plot_drug
    )
  )

dft_over_ex %<>%
  mutate(
    plt_drug_case = purrr::map(
      .x = gg_drug_case,
      .f = \(x) {
        plotly::ggplotly(x, tooltip = 'text')
      }
    )
  )
  


```

### R1.5 Interesting cases to consider

#### Possible sequence, not overlapping

It's common in the breast cancer cohort to see a (seemingly planned) progression of drugs coded as one regimen, but they're not technically overlapping:

```{r, include = T}
dft_over_ex$plt_drug_case[[1]]
```


```{r, include = T}
dft_over_ex$plt_drug_case[[2]]
```

#### Many stops and starts

This is especially common in the CRC cohort:

```{r, include = T}
dft_over_ex$plt_drug_case[[3]]
```

```{r, include = T}
dft_over_ex$plt_drug_case[[4]]
```

This begs the question of whether we want to combine drug administrations which are close but not quite overlapping.

#### Large buildup of for one line

Occasionally someone would qualify for something like a 7-drug regimen:

```{r, include = T}
dft_over_ex$plt_drug_case[[5]]
```

#### Generally complex

```{r, include = T}
dft_over_ex$plt_drug_case[[6]]
```










## Upcoming work

- Assess Jeremy's drug database to see the overlap with the drug information represented in our cohorts.
- Think about how we can encode cancer types for our cohorts (oncotree, icd, custom text, etc).  What type of information do we have on each one of our cases, and how is it associated to the case (e.g. oncotree -> sample, ICD -> ca_seq, etc.)  How does this associate with Jeremy's semantics?

